\chapter*{Acknowledgement}

\vspace{1\baselineskip}

I would like to begin with a beautiful quote from the great scientist Isaac Newton,
"If I have seen further, it is because I have stood on the shoulders of giants."

\vspace{0.25\baselineskip}
This thesis represents only the continuation of the work that was led by \textbf{Peter Lingauer} and \textbf{Revanth Prakash} before me. Their innovative design of the robotic workcell laid the foundation for the entire project, and without their ideas, this work would not have been possible.
\vspace{0.25\baselineskip}

I am heavily indebted to \textbf{Prof. Dr. Matthias Hien} for believing in me to finish this project and to actually suggest it to be my thesis. His ability to oversee the project's development, ensured that it stayed on track and met all key objectives. I am equally grateful to \textbf{Prof. Dr. -Ing. Peter Firsching} for his consistent support throughout my masters' degree programme and for being my first examiner. His advice on clearly defining the scientific background and thorough guidance in writing the thesis were pivotal in shaping this thesis into its final form.
\vspace{0.25\baselineskip}

\textbf{Heinz Pregler} deserves a special mention for his excellent mentoring abilities as a supervisor and for being always there with his vast practical knowledge. Without him, this project would not have been a success. I would also like to extend my sincere thanks to \textbf{Rami El Smaili}, whose expertise in PLC programming and networking played a crucial role in the operation of the workcell. The team at TCC have showed great interest in this project and I would like to thank them for their suggestions.
\vspace{0.25\baselineskip}

I would like to acknowledge the efforts of contributors who write and manage open source softwares, like ROS and other packages. This project uses a great number of packages that are open-source. Also, big thanks to all the people who provide solutions on ROS and stackoverflow. 
\vspace{0.25\baselineskip}

I would also like to thank my parents for their unconditional support. Their understanding and belief in my abilities have always been a source of inspiration.
Finally, I would like to thank \textbf{Alka} for her constant encouragement to complete what I have started. Her presence has been a tremendous source of strength and motivation throughout this phase.
\vspace{0.25\baselineskip}

To all who have contributed in some way to the realization of this work, I extend my sincerest thanks.