\documentclass{article}
\usepackage{geometry} % Adjusts the page layout
\geometry{a4paper, margin=1in} % Custom margins
\usepackage{amsmath} % For enhanced math features
\usepackage{graphicx} % For including graphics
\usepackage{setspace} % For spacing settings

\title{Master's Thesis \\ Robotic Workcell for Automated Bending Process}
\author{Shivam, Shivam \\ Matriculation Number: 12201775}
\date{Cham, 31 July, 2024}

\begin{document}

\maketitle
\begin{center}
\Large{Deggendorf Institute of Technology, Campus Cham} \\
\Large{Faculty of Applied Natural Sciences and Industrial Engineering} \\
\Large{Master of Mechatronics and Cyber-Physical Systems}
\end{center}

\vspace{1cm}

\textbf{First Examiner:} \\
Prof. Dr.-Ing. Peter Firsching

\vspace{1cm}

\section*{Declaration of Originality}
\begin{enumerate}
    \item I hereby declare that I have written this master's thesis independently and have not submitted this thesis for any other examination purposes. I have not used any references or materials other than those mentioned in the bibliography and have marked all literal and analogous citations.
    
    \vspace{0.5cm}
    \begin{flushright}
    Cham, (date) \\
    \vspace{0.5cm}
    Signature of student
    \end{flushright}

    \item I agree that my master's thesis may be made available to a broader public by the DIT library. Therefore, I will hand in a further hard-bound copy of my master's thesis.
    
    \vspace{0.5cm}
    \textit{Yes} \hspace{2cm} \textit{No}
    
    \vspace{0.5cm}
    \begin{flushright}
    Cham, (date) \\
    \vspace{0.5cm}
    Signature of student
    \end{flushright}
    
    \item I declare and take the responsibility that I am the exclusive owner of all rights concerning the master's thesis, including the right of disposal concerning drafts and attached illustrations, plans, or similar materials. I affirm that no third-party rights or claims will be made upon making this master's thesis publicly available.
\end{enumerate}

\vspace{1cm}

\section*{Public Accessibility Approval}
To be filled in by the first examiner if the author agrees with public accessibility of the master's thesis:

\vspace{0.5cm}
Adding a copy of the master's thesis into the stock of the library and the loan of this copy is: \textit{Approved} \hspace{1.5cm} \textit{Not Approved}

\vspace{1cm}
\begin{flushright}
Cham, (date) \\
Signature of First Examiner
\end{flushright}

\end{document}