After the integration tests of each bending operation, the program for each bending stage is compiled together to create a main program which cycles through all bending operations for the test sheet metal part. After all six bending operations on the test part, KR1410 robot loads the sheet in the drawer of storage station.
The main program is based on the flowchart \ref{tab:flowchart} and uses the variables shared with the PLC (as shown in table \ref{tab:kr1410-to-plc} and \ref{tab:plc-to-kr1410}) to perform the bending.

A cycle starts when a new sheet is requested by the KR1410. It ends with the placement of bent sheet in the drawer of the shelf. After all the optimizations for trajectory planning in teach pendant, the cycle time comes out to be around 4 minutes and 10 seconds with all inspection jobs. Without any inspection, the cycle time reduces to 3 minutes and 40 seconds. An inspection is not done for all parts. After every five parts, one part is selected for inspection. This is done in order to reduce the production time.

The performance of the bending process is evaluated in the following sections using the calibration results, inspection assessment and reviewing the bending operation.

\section{Calibration Results}
\label{sec:calibration-results}
\input{6. System Integration and Testing/6.3 Performance Evaluation/calibration-results.tex}
\FloatBarrier  % Force all figures of the first section to be placed before the next section

\section{Inspection Assessment}
\label{sec:inspection-assessment}
\input{6. System Integration and Testing/6.3 Performance Evaluation/inspection.tex}
\FloatBarrier  % Force all figures of the first section to be placed before the next section

\section{Bending Operation Review}
\label{sec:calibration-results}
\input{6. System Integration and Testing/6.3 Performance Evaluation/bending-review.tex}
\FloatBarrier  % Force all figures of the first section to be placed before the next section


