A bending machine that is manufactured in 2005 and no longer in production is chosen for this project.
The bending machine from AMADA is a manual hydraulic press brake that is operated by foot pedal.
It does not comes with a system that allows for automated bending process.
Table \ref{tab:machine_specifications} shows the technical specifications of the bending machine.

% Table for bending machine details
\begin{table}[h!]
    \centering
    \renewcommand{\arraystretch}{1.2} % Adjusts row height
    \small
    \begin{tabular}{ll}
        {\textbf{Description}} & {\textbf{Value}} \\
        \hline
        \textbf{Model} & HFP 50-20 \\
        \textbf{Manufacturer} & \hyperref[acro:AMADA]{AMADA} (France) \\
        \textbf{Year of manufacture} & 2005 \\
        \textbf{Drive} & Hydraulic press brake \\
        \textbf{Pressing capacity} & 500 kN \\
        \textbf{Working length} & 2090 mm \\
        \textbf{Distance between frames} & 1665 mm \\
        \textbf{\hyperref[acro:CNC]{CNC} control} & AMADA AMNC \hyperref[acro:3D]{3D}-graphic \\
        & with \hyperref[acro:TFT]{TFT} color screen \\
        \textbf{controlled axes} &  Y1/Y2; X1/X2; R1/R2; Z1/Z2 \\
        \textbf{Open height} & 470 mm \\
        \textbf{Stroke} & 200 mm \\
        \textbf{Bending Speed} & 10 mm/s \\
        \textbf{Approach Speed} & 100 mm/s \\
        \textbf{Return Speed} & 100 mm/s \\
        \textbf{Laser monitoring} & FIESSLER \\
        \textbf{Length x width x height} & 3458 mm x 2450 mm x 2450 mm \\
        \textbf{Weight} & 4850 kg \\ \hline
    \end{tabular}
    \caption{Bending Machine Technical Specifications (Source: \cite{bmspecifications})}
    \label{tab:machine_specifications}
\end{table}

The AMADA bending machine allows for programming the 5-axis backgauge in the bending machine. It means
for a specific bending operation, the tool and die the 5-axis backgauge
moves in position accordingly and holds the sheet metal part in place. It is also possible to change bending operation by selecting the bending operation number
from the terminal. This is done by the controller \textit{i.e.} AMNC of the press brake.

It is also possible to quickly change a tool in the bending machine. It has a punch holder system  which allows quick and secure tool changes.
The hydraulic system provides the force needed for the bending operations. The hydraulic system does not have any load upto a set point below which
it start bending. This allows for an extremely fast approach and return speeds. \cite{amada-machine}

The bending machine has a laser monitoring device as shown in \ref{fig:bending_machine}
This device from \textbf{Fiessler GmbH} come pre-installed with the bending machine and is a press brake safety measure. It stops the closing of bending machine if a finger or something else is detected
inside the bending machine.

